Collective excitations in the 2- and 3-dimensional extended Hubbard model

### 2023-11-27 paper/main.tex
plotting

\begin{figure*}
    \centering
    \includegraphics[width=.98\textwidth]{plots/resolvent_overview.pdf}
    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
    The left edge of the plots is at $-0.05$ rather than $0$ in order to improve the visibility of the phase peak.
    The shaded area marks the two-particle continuum.
    The panels (a), (b), and (c) show the spectral functions in the SC, CDW, and AFM phases, respectively.}
    \label{fig:resolvent_overview}
\end{figure*}

@@

in various phases and afterward, we will describe the behaviour of the occurring modes as the system approaches a phase transition.
\newline
Firstly, all of the aforementioned operators are (anti-)Hermitian. Therefore, their commutator $[A^\dagger, A]$ vanishes.
Thus, abiding by the sum rule $\int_{-\infty}^\infty \mathcal{A}_{AB} (\omega) \mathrm{d}\omega = \langle [A^\dagger, A] \rangle = 0$ \cite{rickayzen80},
all spectral functions must be symmetrical about $\omega=0$. Therefore, we will only show the $\omega \geq 0$ in our plots.
\newline
Multiple spectral functions in the SC, CDW, and AFM phases are shown in \autoref{fig:resolvent_overview}.

\subsection{CDW-AFM transition}

>>>>

@@

in the SC and CDW phase and afterward, we will describe the behaviour of the occurring modes as the system approaches a phase transition.
\newline
Firstly, all of the operators mentioned in \eqref{eqn:resolvent_bases} are (anti-)Hermitian. 
Therefore, their commutator $[A^\dagger, A]$ vanishes and, 
abiding by the sum rule $\int_{-\infty}^\infty \mathcal{A}_{A^\dagger A} (\omega) \mathrm{d}\omega = \langle [A^\dagger, A] \rangle = 0$ \cite{rickayzen80},
all spectral functions must be symmetrical about $\omega=0$. 
For this reason, we will only show the $\omega \geq 0$ in our plots.
\newline
The corresponding spectral functions in the SC and CDW phases are shown in \autoref{fig:resolvent_overview_SC}.
We chose $U=-2$ for all plots and $V=\pm0.1$.

\begin{figure*}
    \centering
    \includegraphics[width=.98\textwidth]{plots/resolvent_overview_SC_CDW.pdf}
    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
    The left edge of the plots is at $-0.05$ rather than $0$ in order to improve the visibility of the phase peak.
    The shaded area marks the two-particle continuum.
    The panels (a), (b), and (c) show the spectral functions in the SC and CDW phases, respectively.}
    \label{fig:resolvent_overview_SC}
\end{figure*}

\subsection{AFM-CDW transition}

Similar to the previous section, we will first show the general form of the spectral functions with respect to the operators \eqref{eqn:resolvent_bases}.
They are depicted in \autoref{fig:resolvent_overview_AFM}, choosing $V=1$ for the square lattice and $V=0.5$ for the simple cubic lattice.
For the CDW phase (panel a) we chose $V=4.1$ and for the AFM phase (panel b) $V=3.9$.

\begin{figure*}
    \centering
    \includegraphics[width=.98\textwidth]{plots/resolvent_overview_AFM_CDW.pdf}
    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
    %The left edge of the plots is at $-0.05$ rather than $0$ in order to improve the visibility of the phase peak.
    The shaded area marks the two-particle continuum.
    The panels (a) and (b) show the spectral functions in the CDW and AFM phases, respectively.}
    \label{fig:resolvent_overview_AFM}
\end{figure*}
